Live and Let Die? (Delayed Issues not Harder to Resolve)

### 2015-08-17 lucas.tex
syncing

Summary statistics for the agreement and applicability scores for the RqtsErr and PhaseDelay laws are presented in Figure~\ref{fig:survey_results}. Responses whose Applicability response was ''I don't know'' are omitted from analysis.

@@

Researcher survey \\\hline 
Process maturity improves output & 4 & 4.0 & 4 & 4.0 & 4 \\
\textbf{Rqts errors are most expensive...} & 30 & 3.8 & 4 & 3.8 & 4   \\ 
80-20 rule (defects to modules) & 6 & 3.7 & 4 & 3.5 & 4 \\
\textbf{PhaseDelay} & 30 & 3.6 & 4 & -- & --  \\ 
Missing reqts are hardest to fix & 7 & 3.6 & 4 & 3.7 & 4 \\
Adding manpower to a late project & 4 & 3.5 & 4 & 3.5 & 4 \\
Inspections can remove 90\% of defects & 7 & 3.4 & 4 & 3.6 & 3 \\
Reuse increases prod. and qual. & 6 & 3.3 & 4 & 3.0 & 4 \\
OO-programming reduces errors & 6 & 3.2 & 4 & 2.7 & 3 \\
Most time is spent removing errors & 6 & 2.8 & 3 & 3.2 & 4 \\ 
Smaller changes have higher error density & 4 & 2.8 & 3 & 4.0 & 4 \\
A developer is unsuited to test own code & 7 & 2.1 & 2 & 2.4 & 3
\end{tabular}

@@

Both  practitioners and researchers  strongly believed in RqtsErr (in both sets of responses, RqtsErr, received  scores higher than most
other laws. Further, in the case of practitioners, this law was rated
as the single most believed effect. 
%The free response texts, most participants agreed that addressing errors %%late may mean system redesign unless the system and the affected %equirement are simple/trivial. Further, any changes to the production %ystem have additional complexity (compared to changes while system in %evelopment) due to users, data existence, and architecture dependencies. 
Caveat: in the free repsonse texts, we note that the researchers who disagreed with the law generally asserted that requirements change can be expensive, but that depends on the process used (e.g., agile vs. waterfall) and the adaptability of the system architecture.

>>>>

Summary statistics for the agreement and applicability scores for the RqtsErr and DelayedIssueEffect laws are presented in Figure~\ref{fig:survey_results}. Responses whose Applicability response was ''I don't know'' are omitted from analysis.

@@

Researcher survey \\\hline 
Process maturity improves output & 4 & 4.0 & 4 & 4.0 & 4 \\
\textbf{Rqts errors are most expensive...} & 30 & 3.8 & 4 & 3.8 & 4   \\ 
80-20 rule (defects to modules) & 6 & 3.7 & 4 & 3.5 & 4 \\
\textbf{DelayedIssueEffect} & 30 & 3.6 & 4 & -- & --  \\ 
Missing reqts are hardest to fix & 7 & 3.6 & 4 & 3.7 & 4 \\
Adding manpower to a late project & 4 & 3.5 & 4 & 3.5 & 4 \\
Inspections can remove 90\% of defects & 7 & 3.4 & 4 & 3.6 & 3 \\
Reuse increases prod. and qual. & 6 & 3.3 & 4 & 3.0 & 4 \\
OO-programming reduces errors & 6 & 3.2 & 4 & 2.7 & 3 \\
Most time is spent removing errors & 6 & 2.8 & 3 & 3.2 & 4 \\ 
Smaller changes have higher error density & 4 & 2.8 & 3 & 4.0 & 4 \\
A developer is unsuited to test own code & 7 & 2.1 & 2 & 2.4 & 3
\end{tabular}

@@

Both  practitioners and researchers  strongly believed in RqtsErr (in both sets of responses, RqtsErr, received  scores higher than most
other laws. Further, in the case of practitioners, this law was rated
as the single most believed effect. 
%The free response texts, most participants agreed that addressing errors %%late may mean system redesign unless the system and the affected %equirement are simple/trivial. Further, any changes to the production %ystem have additional complexity (compared to changes while system in %evelopment) due to users, data existence, and architecture dependencies. 
Caveat: in the free reponse texts, we note that the researchers who disagreed with the law generally asserted that requirements change can be expensive, but that depends on the process used (e.g., agile vs. waterfall) and the adaptability of the system architecture.

### 2015-08-17 phaseDelay.tex
syncing

\begin{figure}[!b]

@@

It would be convenient to offer the last paragraph as the conclusion of this study
(two of our authors, Nichols and Shull,  work at the organization that invented and promoted TSP).
 However, we cannot endorse such a conclusion:
 \bi
 \item
We view TSP as a better way to
 {\em monitor} the activities {\em of  existing projects}. That is, TSP
 does not radically change a project, it just offers a better way to log the activity within
 that project. 
 \item
 Our 171 project contain examples of a wide variety
 of systems (e-commerce web portals and  banking systems) run in a variety of
 ways (agile or  waterfall or some combination of the two). Hence, rather
 than being unduly  biased in some manner,
 we view our 171 projects as a large sample of current industrial processes for software
 development.
 \ei
Another way to discount this result is to say we are only reporting on small to medium-size
projects, and the real impact of delayed issues is on very large projects.
There certainly exists another class of very large software project where early requirements
errors would be catastrophic for later development. For example, when NASA launches deep space missions,
each of those satellites are special-purpose, uniquely-built devices built by a large contractor
population. Such systems are very hard to reconfigure halfway through the development.

>>>>

\begin{figure}[!t]

@@

It would be convenient to offer the last paragraph as the conclusion of this study
(two of our authors, Nichols and Shull,  work at the organization that invented and promoted TSP).
 However, we cannot endorse such a conclusion:
 \bi
 \item
We view TSP as a better way to
 {\em monitor} the activities {\em of  existing projects}. That is, TSP
 does not radically change a project, it just offers a better way to log the activity within
 that project. 
 \item
 Our 171 project contain examples of a wide variety
 of systems (e-commerce web portals and  banking systems) run in a variety of
 ways (agile or  waterfall or some combination of the two). Hence, rather
 than being unduly  biased in some manner,
 we view our 171 projects as a large sample of current industrial processes for software
 development.
 \ei
Another way to discount this result is to say we are only reporting on small to medium-size
projects,
(see
\fig{dist}:  median
effort was was  
271 days). 
There certainly exists another class of very large software project where early requirements
errors would be catastrophic for later development. For example, when NASA launches deep space missions,
each of those satellites are special-purpose, uniquely-built devices built by a large contractor
population. Such systems are very hard to reconfigure halfway through the development.
